MsCcHSFeed Outline

### 2022-02-23 MsCcHSFeedOutlineDec15.Rmd
reran wasp emergence stats with ln(#emerged +1)

datawasp$num.w.tot <- datawasp$num.w.coc + datawasp$num.w.larvae
datawasp$percent <- (datawasp$num.w.eclos) / (datawasp$num.w.tot)
```

@@

```{r}
waspbinom <- glm(percent ~ food, family = "binomial", weights = num.w.tot, data = datawasp)

@@

```{r}
waspemerge <- lm(num.w.tot ~ food, data = datawasp)

summary(waspemerge)
```

```{r}
waspemergetreat <- lm(num.w.tot ~ treatment, data = datawasp)

summary(waspemergetreat)
```

>>>>

datawasp$num.w.tot <- datawasp$num.w.coc + datawasp$num.w.larvae
datawasp$percent <- (datawasp$num.w.eclos) / (datawasp$num.w.tot)
datawasp$ln.w.tot <- log(datawasp$num.w.tot + 1)
```

@@

```{r}
waspbinom <- glm(percent ~ food*treatment, family = "binomial", weights = num.w.tot, data = datawasp)

@@

```{r}
waspemerge <- lm(ln.w.tot ~ food*treatment, data = datawasp)

summary(waspemerge)

anova(waspemerge)
```
